### 2025-11-16 thesis/theoretical-foundations/index.tex
Add theory sections i need to write
Rewrite the theory section intro

This section serves as an introduction to the theoretical concepts utilized in this thesis. It is meant to establish a
baseline of understanding for the design, implementation and evaluation phases. It briefly covers relational database theory
(incl. SQL), machine learning fundamentals and their subsequent application for large language models.

\subimport{}{relational-theory.tex}
\subimport{}{machine-learning.tex}
\subimport{}{llms.tex}

%\subsection{Problem Decomposition}

%\subsection{Requirements}

% Conceptual Design

%\subsection{System Design}

%\subsubsection{Architecture Design}

%\subsection{Technical Implementation Strategies}

>>>>

This section introduces the theoretical concepts needed for understanding
\textsc{Natural}'s design and implementation sections. It covers relational
database theory, machine learning fundamentals, large language models, natural
language processing, embeddings and graph theory.

These foundations directly support the system's core functions: example
selection ($\sigma$), schema subsetting ($\phi$), query projection ($\pi$),
self-refinement ($\rho$), and voting ($\nu$).

\subimport{}{relational-theory.tex}
\subimport{}{machine-learning.tex}
\subimport{}{llms.tex}
\subimport{}{nlp.tex}
\subimport{}{graphs.tex}
